libcxx

### 2016-11-30 other/libcxx-slides.tex
abstract

\frame{\frametitle{libcxx-performance analysis}
  \begin{itemize}
  \item Improving standard library algorithms like string::find, basic_streambuf::xsgetn
  \item inlining the constructor and destructor of std::string
  \item systematic analysis of attributes in the standard library
  \item comparative analysis of clang-libc++ vs. gcc-libstdc++ on representative benchmarks.
  \item clang+libc++ vs. gcc+libstdc++ performance update. Constructor of vector in libstdc++ contains memcpy
    in the final assembly.
  \end{itemize}

>>>>

\frame{\frametitle{libcxx-performance analysis}

Abstract: We will discuss the improvements and future work on libcxx. This
includes the improvements on standard library algorithms like string::find and
basic_streambuf::xsgetn. These algorithms were suboptimal and we got huge
improvements after optimizing them. Similarly, we enabled the inlining of
constructor and destructor of std::string. We will present a systematic analysis
of function attributes in libc++ and the places where we added missing
attributes. Finally, we will present a comparative analysis of clang-libc++
vs. gcc-libstdc++ on representative benchmarks

Keywords: libc++, libstdc++, C++, performance analysis, function attributes

  \begin{itemize}
  \item Improving standard library algorithms like string::find, basic_streambuf::xsgetn
  \item inlining the constructor and destructor of std::string
  \item systematic analysis of attributes in the standard library
  \item comparative analysis of clang-libc++ vs. gcc-libstdc++ on representative benchmarks.
  \item clang+libc++ vs. gcc+libstdc++ performance update. Constructor of vector in libstdc++ contains memcpy
    in the final assembly.
  \end{itemize}
